Methods paper for erosion

### 2017-12-18 docs/methods/erosion_methods.tex
worked on intro section

@@

For simplicity, we introduce the variables
\begin{align}
\label{eq:M}
& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
\label{eq:N}
& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
\label{eq:elfun}
& \elfun = \frac{2 \pi  \mean{\atau}}{L}
%\frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
\end{align} 
Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
\begin{equation}
\label{eqn:thetaevo1}
\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
\end{equation}
Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}. This is the key to the {\thL} method, and allows us to use very stable, implicit methods for this stiff term.

>>>>

\paragraph{Contributions}

\paragraph{Limitations} There are two main limitations of the current
work.  First, the flow is assumed to be two-dimensional.  Although
several flows can be described to good accuracy under a two-dimensional
approximation, certain phenomena occur only in three-dimensional.  The
boundary integral equation formulation for the fluid solver exists, and
the main challenges of a BIE solver have been addressed by other groups
including surface representation~\cite{yin-bir-zor2006,
vee-rah-bir-zor2011}, near-singular integration~\cite{yin-bir-zor2006,
kli-tor2016b}, and fast summation methods~\cite{yin-bir-zor2004,
ros-ols2015}.  The more significant challenge of extending our work to
three dimensions is guaranteeing that the mesh does not become
distorted, which can be done, for example, by using an extension of the
two-dimensional {\thL} formulation~\cite{amb-sie-tlu2013}.

The second limitation is that the eroding bodies are fixed.  While
mobile eroding bodies have been considered~\cite{Mitchell2016}, only a
single body is simulated.  When multiple bodies are present, especially
in dense suspensions, numerical errors can cause bodies to unphysically
come into contact.  However, by including a small force and
torque~\cite{lu-rah-zor2017}, contact can be avoided.

\paragraph{Related work}

\paragraph{Outline of the paper}

@@

For simplicity, we introduce the variables
\begin{align}
\label{eq:M}
& \Mterm = - 2 \pi \mean{\thalpha \Vn} \\
\label{eq:N}
& \NLterm = \frac{2 \pi}{L} \left( \pderiv{\atau}{\alpha} + \thalpha \Vs \right) \\
\label{eq:elfun}
& \elfun = \frac{2 \pi  \mean{\atau}}{L}
%\frac{4\pi^2}{L^{2} \log \left(2\pi/L \right)}
\end{align} 
Then Eq.~\eqref{eqn:thetaevo0} can be rewritten as
\begin{equation}
\label{eqn:thetaevo1}
\pderiv{\theta}{t} = \eps \elfun \ppd{\theta}{\alpha} + \NLterm
\end{equation}
Note that the highest-order, i.e.~stiff, term in Eq.~\eqref{eqn:thetaevo1} is {\em quasi-linear}. This is the key to the \thL method, and allows us to use very stable, implicit methods for this stiff term.
